### 2015-03-29 Kokkos_PG_MachineModel.tex
Rewrite chapter heading text to clean up.

\chapter{Machine model}
\label{C:Model}

After reading this chapter, you will understand the abstract model of
a shared-memory parallel computer which underlies Kokkos.  
Respecting the abstract machine model ensures performance portability.
The model has two components:
\begin{itemize}
\item \emph{Memory spaces}, in which data live
\item \emph{Execution spaces}, which execute parallel operations using
  data in one or more memory spaces
\end{itemize}
All code that uses Kokkos involves relations between memory and execution spaces.
% A given execution space may or may not be able to access data in a
% given memory space.  Users can ask Kokkos if it can.  Users may also
% copy data between any two different memory spaces by using
% \lstinline!deep_copy!.

\section{Motivation}\label{S:Model:Motivations}

>>>>

\chapter{Machine Model}
\label{C:Model}

After reading this chapter you will understand the abstract model
of a parallel computing node which underlies the design choices
and structure of the Kokkos framework. The machine model ensures
the applications written using Kokkos will have portability across
architectures while being performant on a range of hardware.\\
\\
\noindent
The machine model has two important components:
\begin{itemize}
\item \emph{Memory spaces}, in which data structures can be allocated
\item \emph{Execution spaces}, which execute parallel operations using
  data from one or more memory spaces
\end{itemize}

\section{Motivations}\label{S:Model:Motivations}
